Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-24 tuningpredictor.tex
Updates from ShareLaTeX

Faced with this information overload,
researchers in empirical SE
use  data miners  to (e.g.) generate 
defect predictors from static code measures.
Such   measures can be
automatically extracted from the code base, with very little effort
even for very large software systems~\cite{nagappan05}. 
In addition, they have  some generality
across multiple projects: e.g. defect
predictors developed at NASA~\cite{me07b} have also been successfully
applied in Turkey~\cite{tosun09}.
Such detectors reduce the effort required for 
defect prediction: if 
inspection teams let themselves be guided by defect predictors then
they can find 80\% to 88\% of the defects
after inspecting  20\% to 25\% of the code~\cite{ostrand04,tosun10}.

@@

The results of this paper show that neither of these points is supportable, att least when learning
defect detectors from static code attributes since:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
%\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & 30 &         & {\bf 89} & {\rfour} & 27 &         & {\bf 89} & {\rfour} & 39 &         & {\bf 89 }& {\rfour}\\
antV1 & 32 & {\rtwo} & {\bf 74} & {\rfour} & 41 & {\rtwo} & {\bf 74 }& {\rfour} & 43 & {\rtwo} & 0 &        \\
antV2 & {\bf 78} & {\rfour} & {\bf 78} & {\rfour} & 52 &         & 68 & {\rthree} & 66 & {\rtwo} & 67 & {\rtwo}\\
camelV0 & {\bf 83} & {\rfour} & {\bf 83} & {\rfour} & 26 &         & 33 &         & 34 &         & 45 & {\rone}\\
camelV1 & 22 &         & {\bf 28} & {\rfour} & 23 &         & 24 & {\rone} & {\bf 28} & {\rfour} & {\bf 28} & {\rfour}\\
ivy & 16 &         & {\bf 23} & {\rfour} & 18 & {\rone} & 21 & {\rthree} & 21 & {\rthree} & 20 & {\rtwo}\\
jeditV0 & 35 &         & {\bf 75} & {\rfour} & 49 & {\rone} & 56 & {\rtwo} & 50 & {\rone} & 48 & {\rone}\\
jeditV1 & 24 &         & {\bf 87} & {\rfour} & 28 &         & 86 & {\rfour} & 36 &         & 39 & {\rone}\\
jeditV2 & 2 &         & {\bf 98 }& {\rfour} & 3 &         & 18 &         & 5 &         & 5 &        \\
log4j & 94 &         & {\bf 100} & {\rfour} & 97 & {\rtwo} & {\bf 100} & {\rfour} & {\bf 100} & {\rfour} & {\bf 100 }& {\rfour}\\
lucene & 61 &         & 74 & {\rfour} & 67 & {\rone} & 70 & {\rtwo} & 72 & {\rthree} & {\bf 77} & {\rfour}\\
poiV0 & 70 &         & 68 &         & 77 & {\rfour} & 72 & {\rone} & {\bf 79} & {\rfour} & 76 & {\rthree}\\
poiV1 & {\bf  100} & {\rfour} & 90 & {\rthree} & 73 &         & 89 & {\rtwo} & 81 & {\rone} & {\bf 100} & {\rfour}\\
synapse & 66 &         & 66 &         & 71 & {\rone} & {\bf 100} & {\rfour} & 59 &         & 80 & {\rtwo}\\
velocity & 34 &         & 39 & {\rthree} & 34 &         & 40 & {\rfour} & 40 & {\rfour} & {\bf 41} & {\rfour}\\
xercesV0 & 13 &         & {\bf 85} & {\rfour} & 14 &         & 13 &         & 15 &         & 13 &        \\
xercesV1 & {\bf 56} & {\rfour} & 26 &         & 50 & {\rthree} & 26 &         & 41 & {\rtwo} & 26 &        \\
\end{tabular}
\caption{Precision results (best results  shown in {\bf bold}).}
\label{fig:precisionbars}
\end{figure}

@@

These results offer support for the prior conclusions of  
 Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
\bi
\item
Untuned CART is indeed the worst learner (none of its
untuned results are best and {\bf bold}). 
\item 
In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
\ei
Some of the data sets in \fig{precisionbars} proved challenging for all learners;
e.g. the precision results for {\em ivy} are less
that impressive.
To some extent, this is due to
the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).

That said,  tuning can improve those poor performing detectors:
\bi
\item
For {\em xercesV0}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 85\% precision.  
\item A similar pattern can be seen in results from {\em camelV0},   and {\em jeditV2}.
In those two data sets, nearly all the precision values are   low {\em except} for
tuned WHERE that scored 83\% and 98\%.
\ei
Finally, note the  {\em jeditV2} result for the WHERE learner.
Here, tuning changes precision from 2\% to 98\%.

@@

\scriptsize  
~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
ivy & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
log4j & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
lucene & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
synapse & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
velocity & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
\end{tabular}
\caption{F-value results (best results  shown in {\bf bold}).}
\label{fig:fbars}
\end{figure}

@@

noc &		  &    &    &   \\
ca  &    &    &    &    &    &\\   
max\_cc  &    &  1  &    &  1  &    &  2\\
ce  &    &  1  &    &  2  &    &  3\\
moa  &    &  1  &    &  2  &    &  3\\
cbo  &    &  1  &    &  4  &    &  5\\
avg\_cc  &    &  3  &    &  2  &    &  5\\
lcom  &    &  3  &    &  3  &    &  6\\
npm  &    &  5  &    &  4  &    &  9\\
cbm  &  6  &  3  &  4  &  3  &  10  &  6\\
amc  &  4  &  3  &  4  &  5  &  8  &  8\\
rfc  &  4  &  5  &  4  &  9  &  8  &  14\\
ic  &  7  &  4  &  9  &  4  &  16  &  8\\
wmc  &  5  &  6  &  5  &  11  &  10  &  17\\
dit  &  8  &  6  &  8  &  6  &  16  &  12\\
lcom3  &  9  &  7  &  9  &  7  &  18  &  14\\
loc  &  8  &  6  &  9  &  12  &  17  &  18\\
cam  &  9  &  8  &  9  &  10  &  18  &  18\\
dam  &  14  &  9  &  14  &  11  &  28  &  20\\
mfa  &  16  &  11  &  16  &  13  &  32  &  24

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 50 /  77.16 & 1.30 & 60 /  3.47 & 0.07 & 50 /  6.54 & 0.14\\
    antV1 & 50 /  135.16 & 2.33 & 60 /  4.84 & 0.08 & 50 /  8.61 & 0.19\\
    antV2 & 50 /  368.50 & 6.23 & 60 /  6.67 & 0.14 & 50 /  11.75 & 0.40\\
    camelV0 & 50 /  479.03 & 8.25 & 60 /  11.73 & 0.18 & 60 /  15.69 & 0.31\\
    camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
    ivy & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
    jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
    jeditV1 & 50 /  442.35 & 7.48 & 70 /  8.63 & 0.11 & 70 /  15.52 & 0.37\\
    jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
    log4j & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
    lucene & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
    poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
    poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
    synapse & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
    velocity & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
    xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
    xercesV1 & 50 /  759.82 & 13.11 & 50 /  8.62 & 0.14 & 60 /  16.90 & 0.37\\
  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
\end{figure*}

%%%%time for F %%%%%%
\begin{figure*}[!ht]
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 70 / 95.34 & 1.18 & 50 / 3.09 & 0.06 & 60 / 6.89 & 0.13\\
    antV1 & 50 / 130.69 & 2.24 & 50 / 4.47 & 0.08 & 60 / 9.03 & 0.19\\
    antV2 & 50 / 296.68 & 6.66 & 60 / 7.29 & 0.15 & 60 / 12.74 & 0.31\\
    camelV0 & 60 / 496.70 & 8.01 & 60 / 10.43 & 0.17 & 70 / 17.32 & 0.30\\
    camelV1 & 70 / 1732.99 & 23.35 & 60 / 15.93 & 0.22 & 60 / 24.71 & 0.71\\
    ivy & 70 / 58.81 & 1.03 & 70 / 4.07 & 0.06 & 60 / 7.37 & 0.16\\
    jeditV0 & 90 / 412.23 & 5.17 & 70 / 6.59 & 0.08 & 60 / 10.56 & 0.28\\
    jeditV1 & 70 / 425.18 & 6.61 & 60 / 6.15 & 0.10 & 60 / 13.00 & 0.31\\
    jeditV2 & 60 / 398.86 & 6.97 & 50 / 5.90 & 0.12 & 60 / 13.63 & 0.35\\
    log4j & 50 / 68.17 & 1.37 & 60 / 2.46 & 0.04 & 70 / 6.37 & 0.15\\
    lucene & 50 / 147.78 & 2.74 & 50 / 3.79 & 0.07 & 60 / 7.98 & 0.24\\
    poiV0 & 60 / 251.48 & 3.90 & 60 / 5.65 & 0.09 & 70 / 11.25 & 0.30\\
    poiV1 & 60 / 404.96 & 7.22 & 70 / 8.10 & 0.11 & 60 / 12.74 & 0.28\\
    synapse & 50 / 95.37 & 1.80 & 60 / 3.69 & 0.06 & 60 / 7.65 & 0.14\\
    velocity & 60 / 176.80 & 3.40 & 50 / 4.14 & 0.07 & 50 / 7.36 & 0.23\\
    xercesV0 & 60 / 177.48 & 2.34 & 50 / 6.53 & 0.09 & 50 / 14.91 & 0.33\\
    xercesV1 & 50 / 762.28 & 13.33 & 70/ 12.84 & 0.15 & 60/ 16.63 & 0.40\\
  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  ``F''.  }\label{fig:ftimes}
\end{figure*}

>>>>

Faced with this information overload,
researchers in empirical SE
use  data miners  to generate 
defect predictors from static code measures.
Such   measures can be
automatically extracted from the code base, with very little effort
even for very large software systems~\cite{nagappan05}. 
In addition, they have  some generality
across multiple projects: e.g. defect
predictors developed at NASA~\cite{me07b} have also been successfully
applied in Turkey~\cite{tosun09}.
Such detectors reduce the effort required for 
defect prediction: if 
inspection teams let themselves be guided by defect predictors then
they can find 80\% to 88\% of the defects
after inspecting  20\% to 25\% of the code~\cite{ostrand04,tosun10}.

@@

The results of this paper show that neither of these points is supportable, at least when learning
defect detectors from static code attributes since:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
%\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & 30 &   & {\bf 89} &   & 27 &   & {\bf 89} &   & 28 &   & {\bf 89} &  \\
antV1 & 32 &   & {\bf 74} &   & 36 &   & {\bf 74} &   & 41 &   & {\bf 74} &  \\
antV2 & 78 &   & 52 &   & 52 &   & 56 &   & 64 &   & {\bf 100} &  \\
camelV0 & {\bf 83} &   & {\bf 83} &   & 26 &   & 34 &   & 50 &   & 78 &  \\
camelV1 & 22 &   & 81 &   & 24 &   & {\bf 83} &   & 25 &   & 31 &  \\
ivy & 16 &   & {\bf 89} &   & 17 &   & 25 &   & 16 &   & 21 &  \\
jeditV0 & 35 &   & 48 &   & 49 &   & {\bf 61} &   & 44 &   & 50 &  \\
jeditV1 & 24 &   & {\bf 87} &   & 28 &   & 62 &   & 28 &   & 37 &  \\
jeditV2 & 2 &   & {\bf 98} &   & 3 &   & 18 &   & 5 &   & 5 &  \\
log4j & 94 &   & {\bf 100} &   & 97 &   & {\bf 100} &   & 99 &   & {\bf 100} &  \\
lucene & 61 &   & 76 &   & 67 &   & 70 &   & 67 &   & {\bf 77} &  \\
poiV0 & 74 &   & 74 &   & {\bf 79} &   & 75 &   & 77 &   & 78 &  \\
poiV1 & {\bf 100} &   & 75 &   & 73 &   & 89 &   & 82 &   & {\bf 100} &  \\
synapse & 66 &   & 66 &   & 71 &   & {\bf 100} &   & 65 &   & {\bf 100} &  \\
velocity & 34 &   & {\bf 43} &   & 34 &   & 39 &   & 34 &   & 42 &  \\
xercesV0 & 13 &   & {\bf 85} &   & 14 &   & 47 &   & 15 &   & 14 &  \\
xercesV1 & {\bf 56} &   & 26 &   & 49 &   & 26 &   & 49 &   & 26 &  \\
\end{tabular}
\caption{Precision results (best results  shown in {\bf bold}).}
\label{fig:precisionbars}
\end{figure}

@@

These results offer support for the prior conclusions of  
 Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
\bi
\item
Untuned CART is indeed the worst learner (only one of its
untuned results is best and {\bf bold}). 
\item 
In $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
\ei
% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
% e.g. the precision results for {\em ivy} are less
% that impressive.
% To some extent, this is due to
% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).

That said,  tuning can improve those poor performing detectors:
\bi
\item
For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
\item A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
In those two data sets, nearly all the precision values are   low {\em except} for
tuned WHERE that scored 89\% and 85\%.
\ei
Finally, note the  {\em jeditV2} result for the WHERE learner.
Here, tuning changes precision from 2\% to 98\%.

@@

\scriptsize  
~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & 39 &   & 20 &   & 32 &   & 40 &   & {\bf 41} &   & 21 &  \\
antV1 & 11 &   & 5 &   & 38 &   & 49 &   & 37 &   & {\bf 55} &  \\
antV2 & 0 &   & 3 &   & 44 &   & {\bf 48} &   & 47 &   & 46 &  \\
camelV0 & 0 &   & {\bf 91} &   & 9 &   & 28 &   & 4 &   & 31 &  \\
camelV1 & 35 &   & 35 &   & 31 &   & 33 &   & {\bf 37} &   & 33 &  \\
ivy & 28 &   & 32 &   & 28 &   & 30 &   & 27 &   & {\bf 33} &  \\
jeditV0 & 50 &   & {\bf 57} &   & 56 &   & {\bf 57} &   & 56 &   & {\bf 57} &  \\
jeditV1 & 37 &   & 38 &   & 36 &   & 45 &   & 43 &   & {\bf 49} &  \\
jeditV2 & 4 &   & 6 &   & 5 &   & {\bf 9} &   & {\bf 9} &   & 8 &  \\
log4j & {\bf 61} &   & 54 &   & 47 &   & 46 &   & 57 &   & 45 &  \\
lucene & 70 &   & 74 &   & 56 &   & 74 &   & 70 &   & {\bf 75} &  \\
poiV0 & 82 &   & 71 &   & 79 &   & 62 &   & {\bf 83} &   & 73 &  \\
poiV1 & 5 &   & {\bf 78} &   & 21 &   & {\bf 78} &   & 19 &   & {\bf 78} &  \\
synapse & 0 &   & 2 &   & 40 &   & 55 &   & 41 &   & {\bf 56} &  \\
velocity & 51 &   & 51 &   & 49 &   & {\bf 53} &   & 51 &   & 51 &  \\
xercesV0 & 22 &   & 23 &   & 21 &   & {\bf 27} &   & 24 &   & 20 &  \\
xercesV1 & 23 &   & 4 &   & 18 &   & {\bf 47} &   & 18 &   & 40 &  \\
\end{tabular}
\caption{F-value results (best results  shown in {\bf bold}).}
\label{fig:fbars}
\end{figure}

@@

max\_cc& & & &  & & \\
noc& & & & & & \\
ca& & & & & & \\
cbo& & 1& & & & 1\\
moa& & 1& & & & 1\\
ce& & 2& & 1& & 3\\
avg\_cc& & 2& & 2& & 4\\
npm& 1& 2& 1& 1&2 & 3\\
lcom& 1& 2& 1& 1& 2& 3\\
amc& 4& 2& 4& 2& 8& 4\\
cbm& 5& 2& 5& 3& 10& 5\\
rfc& 3& 6& 3& 8& 6& 14\\
wmc& 5& 4& 5& 9& 10& 13\\
dit& 8& 3& 7& 7& 15& 10\\
ic& 8& 3& 8& 6& 16 & 9\\
lcom3& 8& 6& 8& 8&16 & 14\\
cam& 9& 7& 9& 7& 18& 14\\
loc& 9& 5& 9& 11& 18& 16\\
dam& 13& 6& 13& 11& 26& 17 \\
mfa& 16& 9& 16& 9&32 & 18\\

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 50 / 90.18 & 1.57 & 60 / 4.36 & 0.09 & 50 / 8.12 & 0.18\\
    antV1 & 50 / 174.67 & 2.90 & 50 / 6.35 & 0.10 & 50 / 11.77 & 0.27\\
    antV2 & 50 / 403.63 & 6.92 & 70 / 9.71 & 0.16 & 60 / 13.28 & 0.35\\
    camelV0 & 50 / 537.53 & 8.60 & 50 / 9.14 & 0.18 & 50 / 13.73 & 0.31\\
    camelV1 & 60 / 1640.54 & 24.57 & 60 / 17.06 & 0.24 & 70 / 31.53 & 0.73\\
    ivy & 70 / 77.75 & 1.02 & 60 / 3.86 & 0.06 & 50 / 8.00 & 0.17\\
    jeditV0 & 80 / 472.57 & 5.49 & 60 / 6.30 & 0.09 & 70 / 13.01 & 0.30\\
    jeditV1 & 60 / 489.45 & 6.82 & 70 / 7.61 & 0.11 & 60 / 12.87 & 0.32\\
    jeditV2 & 50 / 435.43 & 7.21 & 50 / 6.46 & 0.12 & 90 / 20.34 & 0.37\\
    log4j & 70 / 113.73 & 1.36 & 70 / 3.25 & 0.05 & 60 / 7.07 & 0.16\\
    lucene & 70 / 224.39 & 2.70 & 50 / 4.07 & 0.08 & 50 / 8.87 & 0.26\\
    poiV0 & 60 / 261.06 & 4.00 & 60 / 6.23 & 0.10 & 50 / 10.57 & 0.29\\
    poiV1 & 80 / 607.85 & 7.18 & 60 / 7.69 & 0.13 & 50 / 11.39 & 0.29\\
    synapse & 50 / 116.04 & 1.87 & 60 / 4.07 & 0.05 & 70 / 9.74 & 0.16\\
    velocity & 60 / 195.27 & 2.75 & 60 / 4.49 & 0.06 & 80 / 12.15 & 0.21\\
    xercesV0 & 60 / 143.69 & 2.17 & 70 / 7.26 & 0.09 & 60 / 10.28 & 0.23\\
    xercesV1 & 50 / 794.50 & 13.37 & 50 / 8.24 & 0.15 & 60 / 14.54 & 0.38\\

  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
\end{figure*}

%%%%time for F %%%%%%
\begin{figure*}[!ht]
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 50 / 94.08 & 1.71 & 60 / 4.55 & 0.08 & 60 / 10.79 & 0.21\\
    antV1 & 60 / 193.74 & 3.02 & 70 / 7.77 & 0.09 & 60 / 12.30 & 0.25\\
    antV2 & 80 / 643.94 & 7.59 & 60 / 8.38 & 0.15 & 70 / 16.99 & 0.41\\
    camelV0 & 60 / 662.56 & 9.97 & 60 / 13.19 & 0.23 & 80 / 26.11 & 0.32\\
    camelV1 & 60 / 1800.64 & 24.25 & 50 / 15.02 & 0.28 & 50 / 28.52 & 0.78\\
    ivy & 60 / 69.95 & 1.03 & 50 / 3.35 & 0.08 & 70 / 9.40 & 0.18\\
    jeditV0 & 90 / 553.80 & 5.58 & 50 / 5.58 & 0.09 & 60 / 15.08 & 0.33\\
    jeditV1 & 60 / 519.75 & 8.76 & 50 / 7.43 & 0.13 & 60 / 18.13 & 0.41\\
    jeditV2 & 70 / 621.32 & 8.98 & 50 / 9.71 & 0.15 & 60 / 17.38 & 0.63\\
    log4j & 70 / 125.29 & 1.73 & 50 / 2.90 & 0.06 & 60 / 8.76 & 0.19\\
    lucene & 50 / 221.99 & 3.52 & 50 / 5.20 & 0.10 & 50 / 10.09 & 0.33\\
    poiV0 & 60 / 327.48 & 5.13 & 50 / 6.56 & 0.11 & 50 / 12.88 & 0.36\\
    poiV1 & 50 / 523.85 & 8.95 & 80 / 12.26 & 0.14 & 60 / 19.56 & 0.35\\
    synapse & 70 / 148.23 & 1.91 & 60 / 3.96 & 0.06 & 60 / 8.19 & 0.16\\
    velocity & 50 / 156.51 & 2.75 & 60 / 4.27 & 0.06 & 50 / 7.70 & 0.22\\
    xercesV0 & 60 / 142.83 & 2.01 & 70 / 7.15 & 0.08 & 60 / 9.61 & 0.20\\
    xercesV1 & 50 / 751.92 & 12.98 & 60 / 9.28 & 0.16 & 50 / 12.69 & 0.38\\

  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  ``F''.  }\label{fig:ftimes}
\end{figure*}
